Towards typed repositories of proofs

### 2010-06-18 papers/MIPS2010/abstract.tex
* Reformulation.
git-svn-id: http://gasp.dev.regis-gianas.com/svn/trunk@126 403e655e-980a-47bd-8c60-1ee5348bb6b7
* Institution.
git-svn-id: http://gasp.dev.regis-gianas.com/svn/trunk@127 403e655e-980a-47bd-8c60-1ee5348bb6b7

\author{Matthias Puech \and Yann Régis-Gianas}
\date{}

@@

Practical efforts in the formalization of mathematical results have
naturally led to the questions of how to manage large repositories of
proofs, i.e. what is the \emph{daily workflow} of users of a proof
assistant. How does one elaborate a formal proof? What kind of \emph{a
  posteriori} modification is he prone to doing? What do these
modifications imply on the validity of the whole edifice or, the other
way around, how does one rely on existing work to build up new results?
Many of these questions remain largely unanswered, but the tendency
seems to be to adapt existing methods coming from software
development, as illustrated for example by the introduction of
modules, file-based scripts and separate compilation in proof
assistants like \textsf{Coq}~\citep{CoqDocWeb} or
\textsf{Matita}~\citep{AspertiCTZ07}, the use of
dependency management tools (\textsf{Make}) or version control system
(\textsf{GIT}, \textsf{Subversion}) to build and manage versions of a
project. Both for the development of proofs or programs, these tools
attempt to cope with the fact that most of a mathematician or
programmer's time is actually spent \emph{editing}, not
\emph{writing}.

@@

The \textsf{Twelf} project~\citep{pfenning1999system} is an
implementation of the Logical
Framework~\citep{harper1993framework}. It was used in
\citep{anderson1993program} to devise transformations of proofs in
order to extract efficient programs. Our kernel language reformulates
LF by a syntactic explicitation of dependencies.

>>>>

\author{
\begin{tabular}{cc}
Matthias Puech &
Yann Régis-Gianas \\ 
&
{\small \url{yrg@pps.jussieu.fr}}\\
& 
{\small Laboratoire PPS, équipe ${\pi}r^2$} \\
&
{\small University Paris 7, CNRS, and INRIA}
\end{tabular}
}
\date{}

@@

Practical efforts in the formalization of mathematical results have
naturally led to the question of how to manage large repositories of
proofs, i.e. what is the \emph{daily workflow} of users of a proof
assistant. How does one elaborate a formal proof? What kind of \emph{a
  posteriori} modification is he prone to doing? What do these
modifications imply on the validity of the whole edifice or, the other
way around, how does one rely on existing work to build up new results?
Many of these questions remain largely unanswered, but the tendency
seems to be to adapt existing methods coming from software
development, as illustrated for example by the introduction of
modules, file-based scripts and separate compilation in proof
assistants like \textsf{Coq}~\citep{CoqDocWeb} or
\textsf{Matita}~\citep{AspertiCTZ07}, the use of
dependency management tools (\textsf{Make}) or version control system
(\textsf{GIT}, \textsf{Subversion}) to build and manage versions of a
project. Both for the development of proofs or programs, these tools
attempt to cope with the fact that most of a mathematician or
programmer's time is actually spent \emph{editing}, not
\emph{writing}.

@@

The \textsf{Twelf} project~\citep{pfenning1999system} is an
implementation of the Logical
Framework~\citep{harper1993framework}. It was used in
\citep{anderson1993program} to devise transformations of proofs in
order to extract efficient programs. Our kernel language reformulates
a fragment of LF to make dependencies syntactically explicit.
